---
title: "OSA"
author: "Zihan Wei"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidiverse)
library(pROC)
library(psych)
```

Read-in data from excel
```{r}
library(readxl)
osa <- read_excel("path/osa.xlsx")
head(osa) #display the data head
```


```{r }
#Descriptive statistics of 4 tests
summary(osa[4:7])
```
#Plot the ROCs
```{r}
#Check the plot and AUC value
roc_stop<-roc(osa$OSA,osa$stop,plot = TRUE)
roc_stopA<-roc(osa$OSA,osa$stopA,plot = TRUE)
roc_stopbang<-roc(osa$OSA,osa$stopbang,plot = TRUE)
roc_stopbangA<-roc(osa$OSA,osa$stopbangA,plot = TRUE)
```

#Use paired test to see if two AUCs are significantly different alpha=0.05
```{r}
roc.test(roc_stop,roc_stopA,paired = TRUE)
roc.test(roc_stopA,roc_stopbang,paired = TRUE)
roc.test(roc_stopA,roc_stopbangA,paired = TRUE)
```
The results above show that stopbangA works better than stop and stopA, but no significant different than stopbang

#Unpaired test to see if stopbangA works equally well on male and female
```{r}
{
  roc_SA_m<-roc(osa[osa$GENDER==1,]$OSA,osa[osa$GENDER==1,]$stopbangA)
  roc_SA_f<-roc(osa[osa$GENDER==0,]$OSA,osa[osa$GENDER==0,]$stopbangA)
  roc.test(roc_SA_f,roc_SA_m)
}
```
The result shows no significant difference between male and female using stopbangA


#Find the best cutoff point
```{r}
#Find the best cutoff point of stopbangA, and return the values: specificity, sensitivity, etc.,
coords(roc_stopbangA,'best',best.method="closest.topleft",
       ret=c("threshold", "specificity", "sensitivity", "accuracy",
             "tn", "tp", "fn", "fp", "npv", "ppv", "1-specificity",
             "1-sensitivity", "1-accuracy", "1-npv", "1-ppv",
             "precision", "recall"))
```

Want to see if try method and random forest can do a better job (using python)

